Computer Science House By-Laws

### 2016-02-26 bylaws.tex
Added House Meeting in ByLaws
Located in section 2.B in ByLaws

% BY-LAW II - GENERAL OPERATIONS OF THE HOUSE
\bylaw{General Operations of the House}
\bsection{Standard Operating Session}
The Standard Operating Session for Computer Science House is during the thirty weeks of Fall and Spring semesters. The Summer Sessions, Intersessions, Institute breaks, and all end of Semester Exam Weeks are considered non-standard operating sessions. Unless explicitly stated otherwise, the requirements and expectations deﬁned in the constitution are for the Standard Operating Session.

>>>>

% BY-LAW II - GENERAL OPERATIONS OF THE HOUSE
\bylaw{General Operations of the House}
\bsection{Standard Operating Session}
The Standard Operating Session for Computer Science House is during the thirty weeks of Fall and Spring semesters. The Summer Sessions, Intersessions, Institute breaks, and all end of Semester Exam Weeks are considered non-standard operating sessions. Unless explicitly stated otherwise, the requirements and expectations deﬁned in the constitution are for the Standard Operating Session.
\bsection{House Meeting}
House Meetings occur weekly throughout the Standard Operating Session, all of which are chaired by the Chairman or an Active member chosen  by the Chairman. Throughout proceedings of a House Meeting each Executive Board member will make announcements and updates to inform members of house.
